---
title: "A Prediction of the 2024 U.S. Election"
subtitle: "Prediction Based on MRP Analysis of Harris Lost"
author: 
  - Shanjie Jiao
  - Aman Rana
  - Kevin Shen
thanks: "Code and data are available at: [https://github.com/Jie-jiao05/2024_US_Election.git)."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```


# Introduction

###Overview paragraph
The United States, as the world’s largest economy and most influential country, will hold its presidential election on November 5, 2024. Despite facing domestic challenges such as inflation, low employment rates after the pandemic, and increasing political polarization due to conflicts between the Democratic and Republican parties, which have accelerated internal tensions.As of October 2024, former President Donald Trump has secured the Republican Party nomination. However, after assassination happened on July 14, 2024, many of his supporters have become even more committed to his legacy. Meanwhile, President Joe Biden withdrew from the election on July 21, leading to the nomination of Kamala Harris as the Democratic candidate. These events have made the 2024 U.S. election increasingly complex and unpredictable, further intensifying uncertainty about the future.



###Estimand paragraph
In this paper, multiple linear regression will be used to fit the dataset provide by Five Thirty Eight[use citation] to estimate Trump's election rate. 

###Results paragraph

###Why it matters paragraph：
Due to the United States' hegemonic position and unparalleled global influence, the outcome of the U.S. election will serve as a guiding light for global developments over the next four years, significantly impacting international security, trade, cooperation, and geopolitics. This article aims to provide a clearer analytical framework for political scientists, the general public, journalists, corporate strategists, and anyone globally concerned with the U.S. election.

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data we will discuss the MLR used in the prediction and the result of the MLR with its predictor variables and the response after transformation. @sec-dis the shortcomings of the study and areas for improvement will be described. @sec-A A Deep Dive to a pollster will be conducted, and @sec-B We will given a idealized survey and methodology





# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR] to analysis the data which are extracted from the 2024 U.S. General President Election collected and published by FiveThirtyEight  [@citation later]. This paper will conduct a Multiple Linear Regression to do further prediction. In this model, we take numeric_grade, pollscore, sample_size as predictors, and pct as response. 

## Data Cleaning

To Simplify the dataset we extract the data of the pollater_id, pollster, methodology,  numeric_grade, pollscore, sample_size, pct, and transform Party and Answer into categorical (0=DEM, 1=REP and 0 = Harris, 1=Trump). In oreder to make the pollster more reliable we will only analysis that transparency are over 3  to increase the liability of this survey.

Overview text

## Measurement
	
Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.



Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it. 

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.








# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.  

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.


### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.


# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```




# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this. 

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}


# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows... 

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```



\newpage


# References


